Some Graphical Realizations of Two-Row Specht Modules of Iwahori-Hecke Algebras of the Symmetric Group

### 2019-07-28 tex/Drafts/Draft-1.tex

  {\color{orange} Literature review and motivation goes here.}\cite{Kleshchev}

@@

  \begin{corollary}\label{S irreducibility}
    If $r = 0$, assume $e > 2$.
    \begin{enumerate}[label={(\roman*)}]
      \item Suppose $e > n$.
        Then, $S^{(n+r,n)}$ is irreducible iff $e \nmid l$ for all $r + 2 \leq l \leq n + r + 1$.
      \item Suppose $e \leq n$.
        Then, $S^{(n+r,n)}$ is irreducible iff $e | r + 1$ and $\nu_{e,p}(h_{ab}^\lambda)$ acquires exactly two values.
    \end{enumerate}  
  \end{corollary}
  In the case that $\lambda = (n+r,n)$ and $e$ satisfy hypothesis \eqref{S irreducibility}.(i), say that $\lambda$ is \emph{$e$-top-indivisible}.
  \begin{proof}
    The beginning condition implies that $\lambda$ is $e$-regular, which we will use below.

@@

  Using this, we immediately see that, for any rectangular partition $(m^\ell)$, we have
  \[
    \Res D^{(m^\ell)} \simeq D^{(m^{\ell-1},m-1)}.
  \]
  The non-rectangular two-row case is more complicated, but we may still describe it fully as follows.
  \begin{corollary}\label{D Restrictions}
    Suppose $r > 0$.
    Then, we may characterize the socle of $\Res \, D^\lambda$ as follows:
    \[
      \soc\prn{\Res \, D^{(n+r,n)}} \simeq \begin{cases}
        D^{(n + r - 1,n)} & e \mid r+2\\
        D^{(n + r,n-1)} & e \nmid r+2, \; e \mid r\\
        D^{(n+r-1,n)} \oplus D^{(n+r,n-1)} & e \nmid r+2,r
      \end{cases}
    \]
  \end{corollary}
  \begin{proof}
    This amounts to computations of the hook lengths $\beta(1,2)$ and $\gamma(1,2)$:
    \begin{align*}
      \beta_\lambda(1,2) &= r + 2\\
      \gamma_\lambda(1,2) &= r
    \end{align*}
    Since $2$ is the largest removable number, $D^{(n+r,n-1)} \subset D^{(n+r,n)}$ iff $e \nmid r + 2$.
    Further, if $e \nmid r + 2$, then $D^{(n+r-1,n)} \subset D^{(n+r,n)}$ iff 1 is good iff $e \nmid r$
  \end{proof}

@@

\section{Crossingless Matchings and Specht Modules}\label{Crossingless Matchings Section}
\subsection{Irreducibility of $M$}
\begin{lemma}
  \label{Cyclic}
  Every basis vector in $M_{2n + r}^r$ is cyclic.
\end{lemma}
\begin{proof}
  We have already proven this in the $r = 0$ case, so suppose that $r > 0$.

@@

\subsection{Correspondence}
\begin{proposition}\;

  \begin{enumerate}[label={(\roman*)}]
    \item
    Suppose that $n,r > 0$.
    Then, a filtration of $\Res M_{2n + r}^r$ is given by
    \begin{equation}
      0 \subset M_{2n + r - 1}^{r-1} \subset \Res \, M_{2n + r}^r \label{Filtration}
     \end{equation}
     with $\Res \, M_{2n + r}^r / M_{2n + r - 1}^{r-1} \simeq M_{2n + r - 1}^{r + 1}$. 
    \item
      We have the following isomorphism of representations:
      \begin{equation}
        M_{2n - 1}^1 \simeq \Res \; M_{2n}^0 \label{0 Restriction}
       \end{equation}
  \end{enumerate}
    When the case is type (i) from the irreduibility lemma, this is a composition series.
\end{proposition}
\begin{proof}
  \textbf{(i)}
  Note that we may identify the subrepresentation of $\Res \; M_{2n + r}^r$ having anchor $n$ with $M_{2n + r - 1}^{r-1}$.

@@

\begin{theorem}
  Suppose $e > n + r + 1$.
  Then, $M_{2n + r}^r \simeq S^{(n+r,n)}$.
\end{theorem}
\begin{proof}
  The case $n = 0$ is already proven, so suppose $n > 0$.
  In order to use Proposition \ref{Combinatorics}, suppose either $e \nmid 4$ or $r \neq 0$.

  By irreducibility, we know that $M_{2n + r}^r \simeq D^\lambda$ for some $e$-restricted partition $\lambda$.
  We will prove this inductively; by identification with the trivial and sign representations, the $2n + r = 2$ caseholds, so suppose this is true for $M_{2m + s}^s$ whenever $2m + s < 2n + r$ and $m + s \leq n + r$ (i.e. $e > m + s + 1$).

  By the inductive hypothesis and irreducibility, we have a composition series given by 
  \begin{equation}
    \label{Composition Series} 0 \longrightarrow D^{(n + r - 1,n)} \longrightarrow \Res \, D^\lambda \longrightarrow D^{(n+r,n-1)} \longrightarrow 0
   \end{equation}
  Hence the theorem is given by Proposition \ref{Combinatorics}.

@@

\section{Fibonacci Representations and Quotients of Specht Modules}\label{Fibonacci Section}
We can start our study of $V$ by studying low-dimensional cases.
First, note that $V_{\vs\vp}^2$ is the sign representation $D^{(2)}$ and $V_{\vs\vp}^2$ is the trivial representation $D^{(1)^2}$.

@@

Now let's prove that $V^3_{\vs\vp}$ is irreducible;
this has basis $\cbr{\vs\vp\vs\vp}, \cbr{\vs\vp\vp\vp}$, and the following matrices:
\[
  \rho_{T_1} = \begin{bmatrix}
    \varb & 0\\
    0 & \vara
  \end{bmatrix}; \hspace{20pt}
  \rho_{T_2} = \begin{bmatrix}
    \varc & \vard\\
    \vard & \vare
  \end{bmatrix}.
\]
A subrepresentation must be one-dimensional, and hence an eigenspace of each of these matrices;
since $\varb \neq \vara$, the first has eigenspaces given by the spans of basis elements, and since $\vard \neq 0$, these are not eigenspaces of the second.
Hence $V^3_{\vs\vp}$ is irreducible.
Now we may move on to the general case.
\begin{proposition}
  The representation $V_{\vs\vp} := V^m_{\vs\vp}$ is irreducible.
\end{proposition}
\begin{proof}
  We will prove this inductively in $m$.
  We've already proven it for $V^2_{\vs\vp}$ and $V^3_{\vs\vp}$, so suppose that $V^{m-2}_{\vs\vp}$ is irreducible.

@@

Knowing this, the restriction statements are clear;
$\Res V_{\vs\vp}^m \simeq V_{\vp\vp}^{m-1}$ by considering the last $m-2$ transpositions, and $\Res V_{\vs\vp}^{m-1} \simeq V_{\vs\vp}^{m-1} \oplus V_{\vs\vs}^{m-1}$ by considering the first $m-2$.
Similarly, $\Res V_{\vs\vs}^m \simeq V_{\vs\vp}^{m-1}$ by considering the first $m-2$ transpositions.
This gives that $V \simeq 3V_{\vs\vp} \oplus 2V_{\vs\vs}$.

\begin{corollary}
  The representation $V_{\vs\vs}$ is irreducible.\qed
\end{corollary}

Now we may move on and use Young Tableau to characterize $V$.
Recall that the socle of $D^\lambda$ is given by $\bigoplus\limits_{\mu \xrightarrow{\text{good}} \lambda} D^\mu$,  and that $D^\lambda$ is semisimple iff every $\mu \xrightarrow{\text{normal}} \lambda$ is good.
\begin{theorem}
  The irreducible components of $V$ are given by the following isomorphisms:
     \begin{align*}  
      V^{2n}_{\vs\vs} &\simeq D^{(n,n)}\\ 
      V^{2n-1}_{\vs\vs} &\simeq D^{(n+1,n-2)}\\
      V^{2n}_{\vs\vp} &\simeq D^{(n+1,n-1)}\\
      V^{2n-1}_{\vs\vp} &\simeq D^{(n,n-1)}.
     \end{align*}
\end{theorem}
\begin{proof}
  We will prove this by induction on $n$;
  we have already proven the base case $V^{2}$, so suppose that we have proven these isomorphisms for $V^{2n-2}$.
  We will prove the isomorphisms for $V^{2n-1}$ and $V^{2n}$.

  By irreducibility, $V^{2n-1}_{\vs\vs} \simeq D^{\lambda_{\vs\vs}}$ and $V^{2n-1}_{\vs\vp} \simeq D^{\lambda_{\vs\vp}}$ for some diagrams $\lambda_{\vs\vs}$ and $\lambda_{\vs\vp}$.
  We will show that $\lambda_{\vs\vs} = (n+1,n-2)$ and $\lambda_{\vs\vp} = (n+1,n-1)$.

  First, note that we have \[\Res \; D^{\lambda_{\vs\vs}} \simeq D^{(n,n-2)} \simeq \Res \; D^{(n+1,n-2)}\] and \[\Res \; D^{\lambda_{\vs\vp}} \simeq D^{(n,n-2)} \oplus D^{(n-1,n-1)} \simeq \Res \; D^{(n,n-1)}.\]
  By semisimplicity of $\Res D^{\lambda_{\vs\vs}}$ and $\Res D^{\lambda_{\vs\vp}}$, every normal cell in $\lambda_{\vs\vs}$ and $\lambda_{\vs\vp}$ is good.
  In particular, the only normal number in $\lambda_{\vs\vs}$ is 1.

  For $\lambda_{\vs\vs}$, the only tableaux which can remove a cell to yield $D^{(n,n-2)}$ are $(n+1,n-2)$, $(n,n-1)$, and $(n,n-2,1)$ as illustrated in Figure \ref{OddRes};
  we have already seen that $D^{(n,n-1)}$ does not have irreducible restriction, so we are left with $(n+1,n-2)$ and $\lambda = (n,n-2,1)$.
  We may directly check that $\lambda$ doesn't satisfy this, as we have the following:
  \begin{align*} 
    \beta_\lambda(1,2) &= 3 - 2 + (n-2) = n-1\\
    \beta_\lambda(1,3) &= 3 - 1 + n = n+2\\
    \beta_\lambda(2,3) &= 2 - 1 + 3 = 4.
   \end{align*} 
  At least one of $\beta_\lambda(1,2)$ and $\beta_\lambda(1,3)$ is nonzero, since $\beta_\lambda(1,3) - \beta_\lambda(1,2) = 3 \not\equiv 0 \pmod e$, and hence at least one of $M_2$ and $M_3$ is empty.
  Hence at least one of 2 or 3 is normal in $(n,n-2,1)$, and $\lambda_{\vs\vs} = (n+1,n-2)$.

  For $\lambda_{\vs\vp}$, we immediately see from Figure \ref{OddRes} that the only option is $(n,n-1)$.
  \begin{figure}
    \begin{align*}
      \cbr{
        \begin{gathered}
        \ydiagram{6,3}. \; \;
        \ydiagram{5,4}, \; \;
        \ydiagram{5,3,1}
      \end{gathered} 
    }&\longrightarrow \begin{gathered}
      \ydiagram{5,3}
      \end{gathered}\\
      \cbr{
        \begin{gathered}
          \ydiagram{5,4}
        \end{gathered}
      }&\longrightarrow
      \begin{gathered}
        \ydiagram{5,3},\;\;
        \ydiagram{4,4}.
      \end{gathered}
    \end{align*}
    \caption{
      Illustration of the partitions of $9$ which can, via row removal, yield $(n,n-2)$ alone, or both $(n,n-2)$ and $(n-1,n-1)$.
    }\label{OddRes}
  \end{figure}

  We can perform a similar argument for the $V^{2n}$ case, finding now that 
  \[\Res \; D^{\mu_{\vs\vs}} \simeq D^{(n,n-1)} \simeq \Res \; D^{(n,n)}\] and 
  \[\Res \; D^{\mu_{\vs\vp}} \simeq D^{(n,n-1)} \oplus D^{(n+1,n-2)} \simeq \Res \; D^{(n+1,n-1)}.\]

  Through a similar process, we see that $\mu_{\vs\vp} = (n+1,n-1)$.
  We narrow down $\mu_{\vs\vs}$ to one of $(n,n)$ or $\mu := (n,n-1,1)$, and note that
  \begin{align*} 
    \beta_\mu(1,2) &= 3 - 2 + (n-1) = n\\
    \beta_\mu(1,3) &= 3 - 1 + n = n+2\\
    \beta_\mu(2,3) &= 2 - 1 + 2 = 3
  \end{align*}
  and hence at least one of 2 or 3 is normal, $\Res D^{(n,n-1,1)}$ is not irreducible, and $\mu_{\vs\vs} = (n,n)$, finishing our proof.
\end{proof}
\begin{corollary}
  We have the following isomorphisms of representations:
  \begin{align*} 
    V^{2n} &\simeq 3D^{(n+1,n-1)} \oplus 2D^{(n,n)}\\
    V^{2n - 1} &\simeq 3D^{(n,n-1)} \oplus 2D^{(n+1,n-2)}
  \end{align*}
\end{corollary}

@@

\section{Empirical Results}\label{Empirics Section}

>>>>

  {\color{orange} Literature review and motivation goes here.}

@@

  \begin{corollary}\label{S irreducibility}
    If $r = 0$, assume $e > 2$.
    \begin{enumerate}[label={(\roman*)}]
      \item Suppose $e > n$.
        Then, $S^{(n+r,n)}$ is irreducible iff $e \nmid l$ for all $r + 2 \leq l \leq n + r + 1$.
      \item Suppose $e \leq n$.
        Then, $S^{(n+r,n)}$ is irreducible iff $e | r + 1$ and $\nu_{e,p}(h_{ab}^\lambda)$ acquires exactly two values.
    \end{enumerate}  
  \end{corollary}
  In the case that $\lambda = (n+r,n)$ and $e \nmid r+2,r+3,\dots,n+r+1$, say that $\lambda$ is \emph{$e$-top-indivisible}.
  Since no multiples of $e$ are in an interval of length $n$ in $\NN$, we have $e > n$, so this is precisely case (i) above.
  \begin{proof}
    The beginning condition implies that $\lambda$ is $e$-regular, which we will use below.

@@

  Using this, we immediately see that, for any rectangular partition $(m^\ell)$, we have
  \[
    \Res D^{(m^\ell)} \simeq D^{(m^{\ell-1},m-1)}.
  \]
  The non-rectangular two-row case is more complicated, but we may still describe it fully as follows.
  \begin{corollary}\label{D Restrictions}
    Suppose $r > 0$.
    Then, we may characterize the socle of $\Res \, D^\lambda$ as follows:
    \[
      \soc\prn{\Res \, D^{(n+r,n)}} \simeq \begin{cases}
        D^{(n + r - 1,n)} & e \mid r+2\\
        D^{(n + r,n-1)} & e \nmid r+2, \; e \mid r\\
        D^{(n+r-1,n)} \oplus D^{(n+r,n-1)} & e \nmid r+2,r
      \end{cases}.
    \]
    Further, when $e \nmid r$ or $e \mid r + 2$, $\Res D^{(n+r,n)}$ is semisimple.
  \end{corollary}
  \begin{proof}
    This amounts to computations of the hook lengths $\beta(1,2)$ and $\gamma(1,2)$:
    \begin{align*}
      \beta_\lambda(1,2) &= r + 2\\
      \gamma_\lambda(1,2) &= r
    \end{align*}
    Since $2$ is the largest removable number, $D^{(n+r,n-1)} \subset D^{(n+r,n)}$ iff $e \nmid r + 2$.
    Further, if $e \nmid r + 2$, then $D^{(n+r-1,n)} \subset D^{(n+r,n)}$ iff 1 is good iff $e \nmid r$
  \end{proof}

@@

\section{Crossingless Matchings and Specht Modules}\label{Crossingless Matchings Section}
In the following section, we will analyze the crossingless matchings representation $M_{2n + r}^r$ with the goal of proving $M_{2n + r}^r \simeq S^{(n+r,n)}$ whenever possible.
We begin by proving irreducibility of $M_{2n + r}^r$ in all cases that $(n+r,n)$ is $e$ top-indivisible;
when $p = 2$, this is all cases where $S^{(n+r,n)}$ is irreducible.
This is proven via an inductive process; if $e \nmid n + r + 1$, then $M$ contains no sign subrepresentation, and this allows us to ``project'' down to the case $M_{2(n-1) + r}^r$, and prove irreducibility of $M$ from irreducibility of this space.

Next, we

\subsection{Irreducibility of $M$}
\begin{lemma}
  \label{Cyclic}
  Every basis vector in $M_{2n + r}^r$ is cyclic.
\end{lemma}
\begin{proof}
  We have already proven this in the $r = 0$ case, so suppose that $r > 0$.

@@

\subsection{Correspondence}
The following theorem of Mathas generalizes the characteristic-free version of the classical branching theorem.\cite{Mathas-article}
It will not be necessary for our present proof of the correspondence, but analogy with $M$ is suggestive.
\begin{theorem}[Characteristic-Free Classical Branching Theorem]
  Let $\lambda$ be a partition of $m$ with $\ell$ removable nodes.
  Then, $\Res \, S^\lambda$ has an $\SH_{k,q}(S_{m-1})$-module filtration
  \[
    0 = S^{0,\lambda} \subset S^{1,\lambda} \subset \cdots \subset S^{\ell,\lambda} = \Res S^\lambda
  \]
  such that $S^{t,\lambda} / S^{t-1,\lambda} \simeq S^{\lambda(t)}$ for all $1 \leq t \leq \ell$.\qed
\end{theorem}

If we replace $S^\lambda$ with the appropriate $M_{2n + r}^r$ above, we find the statement of the following proposition.
\begin{proposition}Suppose that $n > 0$.

  \begin{enumerate}[label={(\roman*)}]
    \item
    Suppose that $r > 0$.
    Then, a filtration of $\Res M_{2n + r}^r$ is given by
    \begin{equation}
      0 \subset M_{2n + r - 1}^{r-1} \subset \Res \, M_{2n + r}^r \label{Filtration}
     \end{equation}
     with $\Res \, M_{2n + r}^r / M_{2n + r - 1}^{r-1} \simeq M_{2n + r - 1}^{r + 1}$. 
    \item
      We have the following isomorphism of representations:
      \begin{equation}
        M_{2n - 1}^1 \simeq \Res \; M_{2n}^0 \label{0 Restriction}
       \end{equation}
  \end{enumerate}
    When the case is type (i) from the irreduibility lemma, this is a composition series.
\end{proposition}
\begin{proof}
  \textbf{(i)}
  Note that we may identify the subrepresentation of $\Res \; M_{2n + r}^r$ having anchor $n$ with $M_{2n + r - 1}^{r-1}$.

@@

We've now assembled the basic pieces necessary to prove our correspondence in the case $e > n + r  1$.
Due to some problematic phenomena in the $r = 0$ case, we will initially make an assumption that $e \neq 4$ or $r \neq 0$ so that we may use the combinatorics of Proposition \ref{Combinatorics}.
We will then assume the remaining case $e = 4, r = 0$, and prove our correspondence using process of elimination via the other surrounding cases for $e = 4$.

\begin{theorem}
  Suppose $e > n + r + 1$.
  Then, $M_{2n + r}^r \simeq S^{(n+r,n)}$.
\end{theorem}
\begin{proof}
  The case $n = 0$ is already proven, so suppose $n > 0$.
  In order to use Proposition \ref{Combinatorics}, suppose for now that either $e \nmid 4$ or $r \neq 0$.

  We will prove this inductively; by identification with the trivial and sign representations, the $2n + r = 2$ caseholds, so suppose this is true for $M_{2m + s}^s$ whenever $2m + s < 2n + r$ and $m + s \leq n + r$ (i.e. $e > m + s + 1$).

  By irreducibility, we know that $M_{2n + r}^r \simeq D^\lambda$ for some $e$-restricted partition $\lambda$.
  By the inductive hypothesis and irreducibility, we have a composition series given by the exact sequence
  \begin{equation}
    \label{Composition Series} 0 \longrightarrow D^{(n + r - 1,n)} \longrightarrow \Res \, D^\lambda \longrightarrow D^{(n+r,n-1)} \longrightarrow 0
   \end{equation}
  Hence the theorem is given by Proposition \ref{Combinatorics}.

@@

\section{Fibonacci Representations and Quotients of Specht Modules}\label{Fibonacci Section}
We have difficulty characterizing the Specht module above when it is irreducible.
We may instead attempt to characterize the irreducible quotient $D^\lambda$ of the Specht module.
In particular, note that, whenever $e \leq r + 2$, the restriction $\Res D^{(n+r,n)}$ decomposes into a direct sum of partitions $(m+s,m)$ such that $e \leq s + 2$ and $2m + s = 2n + r - 1$.
This forms a recurrence among these representations, allowing a combinatorial description of their dimension.
In this section we henceforth assume $e = 5$ and note that this recurrence resembles the Fibonacci recurrence;
we follow this to characterize the restriction $D^{(n+r,n)}$ with $r \leq 3$.

\begin{remark}
  Let $d_{m}^{0,3}$ be the dimension $\dim D^{(n,n)}$ with $2n = m$ when $m$ is even, and $\dim D^{(n+3,n)}$ with $2n + 3 = m$ when $m$ is odd.
  Similarly define $d_m^{1,2}$.
  Then, Corollary \ref{D Restrictions} gives
  \begin{align*}
    d_m^{0,3} &= d_{m-1}^{1,2}\\
    d_m^{1,2} &= d_{m-1}^{1,2} + d_{m-1}^{0,3}\\
    &= d_{m-1}^{0,3} + d_{m-2}^{0,3}.
  \end{align*}
  Carefully following this and noting the base cases $d_2^{0,3} = d_2^{1,2} = 1$, one may note that this recurrences proves that $d_m^{1,2} = d_{m+1}^{0,3} = f_n$, where $f_n$ is the $n$th \emph{Fibonacci number}.
  This matches the dimension our Fibonacci subrepresentations, motivating their definition.\qed
\end{remark}

We can start our study of $V$ by studying low-dimensional cases.
First, note that $V_{\vs\vp}^2$ is the sign representation $D^{(2)}$ and $V_{\vs\vp}^2$ is the trivial representation $D^{(1)^2}$.

@@

Now we may prove that $V^3_{\vs\vp}$ is irreducible;
this has basis $\cbr{\prn{\vs\vp\vs\vp}, \prn{\vs\vp\vp\vp}}$, and the following matrices:
\[
  \rho_{T_1} = \begin{bmatrix}
    \varb & 0\\
    0 & \vara
  \end{bmatrix}; \hspace{20pt}
  \rho_{T_2} = \begin{bmatrix}
    \varc & \vard\\
    \vard & \vare
  \end{bmatrix}.
\]
A subrepresentation must be one-dimensional, and hence an eigenspace of each of these matrices;
since $\varb \neq \vara$, the first has eigenspaces given by the spans of basis elements, and since $\vard \neq 0$, these are not eigenspaces of the second.
Hence $V^3_{\vs\vp}$ is irreducible.

These establish the low-dimensional behavior that we will use as base cases below.
The rest of this section will proceed first by proving that $V_{\vs\vp}$ and $V_{\vs\vs}$ are irreducible;
then, we will use combinatorial arguments to prove that these are isomorphic to the correct two-row Specht module quotients.

\begin{proposition}
  The representation $V_{\vs\vp} := V^m_{\vs\vp}$ is irreducible.
\end{proposition}
\begin{proof}
  We will prove this inductively in $m$.
  We've already proven it for $V^2_{\vs\vp}$ and $V^3_{\vs\vp}$, so suppose that $V^{m-2}_{\vs\vp}$ is irreducible.

@@

Now, we may begin considering restrictions:
\begin{lemma}
  The following branching rules hold:
  \begin{align*}
    V^{m-1}_{\vp\vp} \simeq \Res V_{\vs\vp}^m &\simeq V^{m-1}_{\vs\vs} \oplus V^{m-1}_{\vs\vp}\\
    \Res V_{\vs\vs}^m &\simeq V_{\vs\vp}^{m-1}.
  \end{align*}
\end{lemma}
\begin{proof}
  The first line follows by considering the last two $m-2$ transpositions for the left isomorphism, then the first two for the right isomorphism.
  This is well-behaved by Appendix \ref{Algebra}.

  Similarly, the second line follows by considering the last $m-2$ transpositions.
\end{proof}
This immediately gives a rather strong characterization of $V$.
\begin{corollary}
  The representation $V_{\vs\vs}$ is irreducible.\qed
\end{corollary}
\begin{corollary}
  The representation $V$ decomposes into a direct sum of irreducible representations as follows:
  \[
    V \simeq 3V_{\vs\vp} \oplus 2V_{\vs\vs}.
  \]\qed
\end{corollary}

Now we may use these in order to apply Young Tableau to characterize $V$.
\begin{theorem}
  The irreducible components of $V$ are given by the following isomorphisms:
     \begin{align*}  
      V^{2n}_{\vs\vs} &\simeq D^{(n,n)}\\ 
      V^{2n-1}_{\vs\vs} &\simeq D^{(n+1,n-2)}\\
      V^{2n}_{\vs\vp} &\simeq D^{(n+1,n-1)}\\
      V^{2n-1}_{\vs\vp} &\simeq D^{(n,n-1)}.
     \end{align*}
\end{theorem}
\begin{proof}
  We will prove this by induction on $n$;
  we have already proven the base case $V^{2}$, so suppose that we have proven these isomorphisms for $V^{2n-2}$.
  We will prove the isomorphisms for $V^{2n-1}$ and $V^{2n}$.

  By irreducibility, $V^{2n-1}_{\vs\vs} \simeq D^{\lambda}$ and $V^{2n-1}_{\vs\vp} \simeq D^{\mu}$ for some diagrams $\lambda$ and $\mu$.
  We will show that $\lambda = (n+1,n-2)$ and $\mu = (n+1,n-1)$.

  First, note that we have \[\Res \; D^{\lambda} \simeq D^{(n,n-2)} \simeq \Res \; D^{(n+1,n-2)}\] and \[\Res \; D^{\mu} \simeq D^{(n,n-2)} \oplus D^{(n-1,n-1)} \simeq \Res \; D^{(n,n-1)}.\]

  By irreducibility of $\Res D^{\lambda}$, the only normal number in $\lambda$ is 1.
  Further, the only tableaux which can remove a cell to yield $D^{(n,n-2)}$ are $(n+1,n-2)$, $(n,n-1)$, and $(n,n-2,1)$ as illustrated in Figure \ref{OddRes};
  we have already seen that $D^{(n,n-1)}$ does not have irreducible restriction, so we are left with $(n+1,n-2)$ and $\varsigma = (n,n-2,1)$.
  We may directly check that $\varsigma$ doesn't satisfy this, as we have the following:
  \begin{align*} 
    \beta_\varsigma(1,2) &= 3 - 2 + (n-2) = n-1\\
    \beta_\varsigma(1,3) &= 3 - 1 + n = n+2\\
    \beta_\varsigma(2,3) &= 2 - 1 + 3 = 4.
   \end{align*} 
  At least one of $\beta_\varsigma(1,2)$ and $\beta_\varsigma(1,3)$ is nonzero, since $\beta_\varsigma(1,3) - \beta_\varsigma(1,2) = 3 \not\equiv 0 \pmod e$, and hence at least one of $M_2$ and $M_3$ is empty.
  Hence at least one of 2 or 3 is normal in $\varsigma$, and $\lambda = (n+1,n-2)$.

  For $\mu$, we immediately see from Figure \ref{OddRes} that the only option is $(n,n-1)$.
  \begin{figure}
    \begin{align*}
      \cbr{
        \begin{gathered}
        \ydiagram{6,3}. \; \;
        \ydiagram{5,4}, \; \;
        \ydiagram{5,3,1}
      \end{gathered} 
    }&\longrightarrow \begin{gathered}
      \ydiagram{5,3}
      \end{gathered}\\
      \cbr{
        \begin{gathered}
          \ydiagram{5,4}
        \end{gathered}
      }&\longrightarrow
      \begin{gathered}
        \ydiagram{5,3},\;\;
        \ydiagram{4,4}.
      \end{gathered}
    \end{align*}
    \caption{
      Illustration of the partitions of $9$ which can, via row removal, yield $(n,n-2)$ alone, or both $(n,n-2)$ and $(n-1,n-1)$.
    }\label{OddRes}
  \end{figure}

  We can perform a similar argument for the $V^{2n}$ case, finding now that 
  \[\Res \; D^{\lambda'} \simeq D^{(n,n-1)} \simeq \Res \; D^{(n,n)}\] and 
  \[\Res \; D^{\mu'} \simeq D^{(n,n-1)} \oplus D^{(n+1,n-2)} \simeq \Res \; D^{(n+1,n-1)}.\]

  Through a similar process, we see that $\mu' = (n+1,n-1)$.
  We narrow down $\lambda'$ to one of $(n,n)$ or $\varpi := (n,n-1,1)$, and note that
  \begin{align*} 
    \beta_\varpi(1,2) &= 3 - 2 + (n-1) = n\\
    \beta_\varpi(1,3) &= 3 - 1 + n = n+2\\
    \beta_\varpi(2,3) &= 2 - 1 + 2 = 3
  \end{align*}
  and hence at least one of 2 or 3 is normal, $\Res D^{\varpi}$ is not irreducible, and $\lambda' = (n,n)$, finishing our proof.
\end{proof}
\begin{corollary}
  We have the following isomorphisms of representations:
  \begin{align*} 
    V^{2n} &\simeq 3D^{(n+1,n-1)} \oplus 2D^{(n,n)}\\
    V^{2n - 1} &\simeq 3D^{(n,n-1)} \oplus 2D^{(n+1,n-2)}
  \end{align*}
\end{corollary}

@@

\section{Empirical Results}\label{Empirics Section}
In this section we aim both to support conjecture with data and to provide transition matrices wherever possible between our two graphical representaitons.
All data will be generated via tools available on \underline{\href{https://github.com/nataliesstewart/Hecke-Heuristics}{github}}.\footnote{The full URL to the repository is \underline{\href{https://github.com/nataliesstewart/Hecke-Heuristics}{https://github.com/nataliesstewart/Hecke-Heuristics}}.}
